{\it E}nKCF: Ensemble of Kernelized Correlation Filters for Object Tracking in High Speed

### 2017-06-01 bmvc_review.tex
Filters Details Figure Updated
TEXT ADDED

\documentclass{bmvc2k}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools} % mathtools builds on and extends amsmath package
% \usepackage{algorithm}		% http://ctan.org/pkg/algorithms
\usepackage{algpseudocode}	% http://ctan.org/pkg/algorithmicx% Include other packages here, before hyperref.
\usepackage{comment, url}
\usepackage[ruled, vlined, linesnumbered]{algorithm2e}

@@

@@

\subsection{Kernelized Correlation Filter} \label{sec:kcf}
The Kernelized Correlation Filter is a well, known single target
tracking method and its work flow has been detailed in other papers
\cite{henriques2012exploiting,henriques2015high}. This section briefly
goes over the parts of the KCF relevant to this study. Its
computational efficiency is derived from the correlation filter
framework representing training examples as a circulant matrix. The
fact that a circulant matrix can be diagonalized by Discrete Fourier
transform is the key to reduce the complexity of any tracking method
based on correlation filter. The off-diagonal elements become zero
whereas the diagonal elements represent the eigenvalues of the
circulant matrix. The egienvalues are equal to the DFT transformation
of the base sample ($x$) elements. The Kernelized Correlation Filter,
in particular, applies a kernel to $x$ to transform to a more
discriminative domain. The circulant matrix is then formed by applying
cyclic shifts on the kernelized $x$. Such kernelization operation does
not introduce additional complexity to the baseline correlation filter
framework.

>>>>

\documentclass{bmvc2k}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools} % mathtools builds on and extends amsmath package
% \usepackage{algorithm}		% http://ctan.org/pkg/algorithms
\usepackage{algpseudocode}	% http://ctan.org/pkg/algorithmicx% Include other packages here, before hyperref.
\usepackage{comment, url}
\usepackage[ruled, vlined, linesnumbered]{algorithm2e}
\newcommand{\forceindent}{\leavevmode{\parindent=1em\indent}}

@@

{\it YoungWoo : I just did it. Let me know if you see any problem with it.}

@@

\subsection{Kernelized Correlation Filter} \label{sec:kcf}
The Kernelized Correlation Filter is a well, known single target
tracking method and its work flow has been detailed in other papers
\cite{henriques2012exploiting,henriques2015high}. This section briefly
goes over the parts of the KCF relevant to this study. Its
computational efficiency is derived from the correlation filter
framework representing training examples as a circulant matrix. The
fact that a circulant matrix can be diagonalized by Discrete Fourier
transform is the key to reduce the complexity of any tracking method
based on correlation filter. The off-diagonal elements become zero
whereas the diagonal elements represent the eigenvalues of the
circulant matrix. The egienvalues are equal to the DFT transformation
of the base sample ($x$) elements. The Kernelized Correlation Filter,
in particular, applies a kernel to $x$ to transform to a more
discriminative domain. The circulant matrix is then formed by applying
cyclic shifts on the kernelized $x$. Such kernelization operation maintains 
O($nlog(n)$) complexity unlike other kernel algorithms leading to O($n^{2}$) or even higher 
complexities.
